RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-25 introduction.tex
whatever

>>>>

Main requirement is to satisfy these two sets of users: R coders and
managers. They work differently and want different things. What should
the infrastructure look like so they both coexist in peace? If this is
such a fundamental problem, why have other tools not addressed it?
Discuss Shiny (maybe in the disc. section).
